Nested sampling with two objective functions

### 2016-02-09 Paper/ms.tex
Increased figure size
LJ potential

\begin{figure}
\centering
\includegraphics[scale=0.75]{figures/output.png}
\caption{The sequence of discarded particles (yellow) and
points representing the canonical distribution at temperatures
$(T_1, T_2) = (0.1, 1)$ (black).\label{fig:output}}
\end{figure}

@@

@@

Therefore, this is a `doubly intractable' problem, closely related to
those studied (and solved) by \citep{murray}.

@@

BJB initiated the project and explored various ideas which did not work.
EC worked on the biased sampling suggestion in Section~\ref{sec:rationale},
discovered the failure mode in Section~\ref{sec:failure_modes}, ...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{figure}
\centering
\includegraphics[scale=1]{figures/output.png}
\caption{The sequence of discarded particles (yellow) and
points representing the canonical distribution at temperatures
$(T_1, T_2) = (0.1, 1)$ (black).\label{fig:output}}
\end{figure}

@@

Consider $n$ Lennard-Jones atoms confined to the unit cube $[0, 1]^3$.
The position of each atom is given by a vector
$\boldsymbol{r}_i = (x_i, y_i, z_i)$.
The potential energy of any configuration of the atoms is given by
a sum over all pairs of atoms:
\begin{eqnarray}
U_{\rm LJ} &=& \sum_{i=1}^n\sum_{j=(i+1)}^n U_{\rm LJ}
(\boldsymbol{r}_i, \boldsymbol{r}_j)
\end{eqnarray}
where the inter-atomic potential energy is given by:

\begin{eqnarray}
U_{\rm LJ}(\boldsymbol{r}_i, \boldsymbol{r}_j)
&=& 4\epsilon
\left[
\left(\frac{\sigma}{|\boldsymbol{r}_i - \boldsymbol{r}_j|}\right)^12 -
\left(\frac{\sigma}{|\boldsymbol{r}_i - \boldsymbol{r}_j|}\right)^6
\right].
\end{eqnarray}
We adopted the Lennard Jones units by setting $\epsilon=1$ and $\sigma=1$.

@@

Therefore, this is a `doubly intractable' problem \citep{murray}. An integral, whose
result is a function of the parameters, appears in the {\em denominator} of the
target density. However, in our case the integral in the
denominator arises from the prior for the parameters, rather than from the
likelihood function.

@@

BJB initiated the project and explored various ideas which did not work.
EC worked on the biased sampling suggestion in Section~\ref{sec:rationale},
discovered the failure mode in Section~\ref{sec:failure_modes}, and was involved
in many other discussions about the project. RB suggested the statistical
mechanics example and helped BJB to get it working and to interpret the results.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
